A data-intensive assessment of the species-abundance distribution.

### 2015-03-19 defense_pres.tex
Tweaks size of map after fixing.
More presentation work- adds acknowledgements and intro.

\begin{frame}
\titlepage
\end{frame}

@@

\section{Data}

\subsection{Compiled Data}
\subsubsection{Data Collection}
\begin{frame}[shrink=30]
\frametitle{Data}
\begin{table}
\begin{tabular}{l|l} 
 Variable name & Variable definitions\\ 
\hline
 Class & Taxonomic class of species \\
 Family & Taxonomic family of species \\
 Genus & Taxonomic genus of species\\
 Species & Specific epithet of species  \\
 Relative\_abundance & Relative abundance of species \\
 Abundance & Abundance of species \\
 Collection\_Year & Start of collecting \\
 End\_Collection & End of collecting \\
 Site\_Name & Name/description of site \\
 Biogeographic\_region & Biogeographic region \\
 Site\_notes & Additional site information \\ 
\end{tabular}
\caption{List of variables collected.}
\end{table}
\end{frame}

@@

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/chapter3/partial_sites_map.png}
\end{frame}

@@

\section{Acknowledgements}
\subsection{Accessibility}

\end{document}

>>>>

\begin{frame}[t]
\titlepage
\end{frame}

@@

\section{Introduction}
\subsection{What is macroecology?}
\begin{frame}
\frametitle{Macroecology}
One approach to studying ecological patterns and processes.
\begin{itemize}
\item Data intensive.
\item Large scales (spatial, temporal, taxonomic).
\item Search for generality.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Macroecology}
Criticisms of macroecology
\begin{itemize}
\item North American terrestrial bias.
\item Lack of identification of pattern generating mechanisms.
\end{itemize}
\end{frame}

\section{Data}
\subsection{Compiled Data}
\subsubsection{Data Collection}
\begin{frame}[shrink=30]
\frametitle{Data}
\begin{table}
\begin{tabular}{l|l} 
 Variable name & Variable definitions\\ 
\hline
 Class & Taxonomic class of species \\
 Family & Taxonomic family of species \\
 Genus & Taxonomic genus of species\\
 Species & Specific epithet of species  \\
 Relative\_abundance & Relative abundance of species \\
 Abundance & Abundance of species \\
 Collection\_Year & Start of collecting \\
 End\_Collection & End of collecting \\
 Site\_Name & Name/description of site \\
 Biogeographic\_region & Biogeographic region \\
 Site\_notes & Additional site information \\ 
\end{tabular}
\caption{List of variables collected.}
\end{table}
\end{frame}

@@

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
\end{frame}

@@

\section{Acknowledgements}
\begin{frame}[t]{}
\frametitle{Acknowledgements}
~\\ %Adds vertical space for better aesthetics
\small{Funding sources:}
\begin{tiny}
\begin{itemize}
\item USU Department of Biology
\item Intellectual Ventures private funding to Morgan Ernest
\item National Science Foundation CAREER Grant to Ethan White
\item Gordon \& Betty Moore Foundation's Data-Driven Discovery Initiative Grant to Ethan White.
\item USU Graduate School Dissertation Fellowship
\end{itemize}
\end{tiny}
\end{frame}

\begin{frame}{}
\frametitle{Acknowledgements}
The Weecologists
\includegraphics[scale=.3]{../Miscellaneous/Pictures/Phd/whiteboard.png}
\begin{tiny}
(especially Xiao Xiao \& Ken Locey (creator of the whiteboard))
\end{tiny}
\end{frame}

\subsection{Accessibility}
\begin{frame}{}

\end{frame}
\end{document}
